Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 bckground.tex
Answer Shantenu's comments in II and VI

>>>>

\jhanote{In this section we should talk less about PanDA and more about other
WMS -- highlighting the fact that (i) there isn't a comprehensive systems
(design, architecture and execution properties) discussion of other WMS so
difficult to compare}\mtnote{What dimension(s) should we use to argue that WMS are difficult to compare?}
\jhanote{(ii) real comparison should be to the Gliden-in WMS ecosystem and use
this as opportunity to narrate the reasons for the divergence.}\mtnote{From our
meetings with Sergey: Before Run 1, ATLAS management become uncomfortable with
the pace at which other WMS were being developed, loosing trust in their ability
to deliver production-grade capabilities. ATLAS USA decided to go solo and
developed their own solution. PanDA proven to be able to deliver the
usual pilot-based WMS capabilities at the right scale. For that, it was chosen
over other solutions.}
\jhanote{Also might this section be moved towards the rear, as this is  a
practice paper and not a traditional research paper?}\mtnote{Fine with me.}

### 2017-03-27 nge.tex
Answer Shantenu's comments in II and VI

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.} As seen in
\S\ref{sec:panda_deployment}, the absence of wide area network
\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used
for cross data center} connectivity on Titan's worker nodes was one of the
main reasons for PanDA Broker not to implement pilots. As discussed in
\S\ref{sec:panda_titan}, the absence of pilots imposes the static coupling
between MPI scripts submitted to the PBS batch system and detector
simulations, and development tailored to each type of payload that needs to be
executed.

>>>>

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.} As seen in
\S\ref{sec:panda_deployment}, the absence of wide area network
\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used for
cross data center}\mtnote{Every PanDA Pilot has to communicate with PanDA
Server. PanDA Server runs on dedicated resources, outside OLCF. Titan's worker
nodes cannot communicate with PanDA Server because their connectivity is limited
to Titan's network. Do you have a suggestion for an alternative to ``wide
area''?} connectivity on Titan's worker nodes was one of the main reasons for
PanDA Broker not to implement pilots. As discussed in \S\ref{sec:panda_titan},
the absence of pilots imposes the static coupling between MPI scripts submitted
to the PBS batch system and detector simulations, and development tailored to
each type of payload that needs to be executed.
